Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-24 talk/vmil2012/paper.tex
remember to do store sinking
explain store sinking

>>>>

Similarly, stores into the heap are delayed as long as possible.
This can make it necessary to perform these delayed stores
when leaving the trace via a guard.
Therefore the resume data needs to contain a description
of the delayed stores to be able to perform them when the guard fails.
So far no special compression is done with this information.
